---
title: "PowerSim_MoreTrials"
output:
  html_notebook: default
  html: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load functions and reminders 
``` {r Load}

source("./functions/SimData.R")
source("./functions/CompPower.R")
source("./functions/CompPower2.R")

# Run power simulations for different samples sizes and plot power curve
# REMEMBER codes for effects of interest:
# RelY
# RelY:RelX
# RelY:RelX:Condition0 / Complementary condition vs Baseline
# RelY:RelX:Condition1 / Collaborative condition vs Baseline
```

### Define Parameters and Initialize
``` {r Init}

# Choose sample sizes
n_subj <- c(60, 80)

# Initialize dataframes
power_all_df <- data.frame('Power' = numeric(), 'N_Succ'= numeric(), 'N_Trials'= numeric(), 'Lower' = numeric(), 'Upper'= numeric())

power_all_df_2 <-data.frame('Power' = numeric(), 'N_Succ'= numeric(), 'N_Trials'= numeric(), 'Lower' = numeric(), 'Upper'= numeric())

```

### Run Simulation for Effect Size 0.5
```{r NoCluster}
library(lme4)

for (n in n_subj)
{
  
  # Store values and add to dataframe
  outcome <- power_all(J = n, K = 198, C = 3, beta = c(0, -0.5, -0.5, 0.5, 0.5), n.sims = 100)
  power_all_df <- rbind(power_all_df, outcome)
  
}

# Merge with number of subjects
power_all_df <- cbind("N_subj" = n_subj, power_all_df)
print(power_all_df)
```

### Plot power curve RelY
``` {r Plot1}
library(ggplot2)

power_curve <- ggplot(power_all_df, aes(x=N_subj, y=Power_relY*100)) 

power_curve + 
  geom_errorbar(aes(ymin=power_all_df$Lower_relY * 100, ymax=power_all_df$Upper_relY * 100),  color = '#56B4E9') +
  geom_line(size = 1) +
  geom_hline(yintercept = 80, lty = 'dashed', color = 'red', size = 0.5) +
  geom_point(shape = 21, size = 3, color = '#56B4E9', fill = 'white') +
  ylim(0, 100) +
  ylab('Power') +
  xlab('Number of Subjects') 


```

### Plot power curve RelY:RelX
``` {r Plot2}
library(ggplot2)

power_curve <- ggplot(power_all_df, aes(x=N_subj, y=Power_relYrelX*100)) 

power_curve + 
  geom_errorbar(aes(ymin=power_all_df$Lower_relYrelX * 100, ymax=power_all_df$Upper_relYrelX * 100),  color = '#56B4E9') +
  geom_line(size = 1) +
  geom_hline(yintercept = 80, lty = 'dashed', color = 'red', size = 0.5) +
  geom_point(shape = 21, size = 3, color = '#56B4E9', fill = 'white') +
  ylim(0, 100) +
  ylab('Power') +
  xlab('Number of Subjects') 


```
### Plot power curve relY:relX:CondComp
``` {r Plot3}
library(ggplot2)

power_curve <- ggplot(power_all_df, aes(x=N_subj, y=Power_relYrelXcondcomp*100)) 

power_curve + 
  geom_errorbar(aes(ymin=power_all_df$Lower_relYrelXcondcomp * 100, ymax=power_all_df$Upper_relYrelXcondcomp * 100),  color = '#56B4E9') +
  geom_line(size = 1) +
  geom_hline(yintercept = 80, lty = 'dashed', color = 'red', size = 0.5) +
  geom_point(shape = 21, size = 3, color = '#56B4E9', fill = 'white') +
  ylim(0, 100) +
  ylab('Power') +
  xlab('Number of Subjects') 


```

### Plot power curve relY:relX:CondColl
``` {r Plot4}
library(ggplot2)

power_curve <- ggplot(power_all_df, aes(x=N_subj, y=Power_relYrelXcondcoll*100)) 

power_curve + 
  geom_errorbar(aes(ymin=power_all_df$Lower_relYrelXcondcoll * 100, ymax=power_all_df$Upper_relYrelXcondcoll * 100),  color = '#56B4E9') +
  geom_line(size = 1) +
  geom_hline(yintercept = 80, lty = 'dashed', color = 'red', size = 0.5) +
  geom_point(shape = 21, size = 3, color = '#56B4E9', fill = 'white') +
  ylim(0, 100) +
  ylab('Power') +
  xlab('Number of Subjects') 

```

### Run simulation for effect size 0.7

```{r NoCluster2}
library(lme4)

for (n in n_subj)
{
  
  # Store values and add to dataframe
  outcome <- power_all(J = n, K = 198, C = 3, beta = c(0, -0.7, -0.7, 0.7, 0.7), n.sims = 100)
  power_all_df_2 <- rbind(power_all_df_2, outcome)
  
}

# Merge with number of subjects
power_all_df_2 <- cbind("N_subj" = n_subj, power_all_df_2)
print(power_all_df_2)
```


### Plot power curve RelY
``` {r Plot1_2}
library(ggplot2)

power_curve <- ggplot(power_all_df_2, aes(x=N_subj, y=Power_relY*100)) 

power_curve + 
  geom_errorbar(aes(ymin=power_all_df_2$Lower_relY * 100, ymax=power_all_df_2$Upper_relY * 100),  color = '#56B4E9') +
  geom_line(size = 1) +
  geom_hline(yintercept = 80, lty = 'dashed', color = 'red', size = 0.5) +
  geom_point(shape = 21, size = 3, color = '#56B4E9', fill = 'white') +
  ylim(0, 100) +
  ylab('Power') +
  xlab('Number of Subjects') 


```

### Plot power curve RelY:RelX
``` {r Plot2_2}
library(ggplot2)

power_curve <- ggplot(power_all_df_2, aes(x=N_subj, y=Power_relYrelX*100)) 

power_curve + 
  geom_errorbar(aes(ymin=power_all_df_2$Lower_relYrelX * 100, ymax=power_all_df_2$Upper_relYrelX * 100),  color = '#56B4E9') +
  geom_line(size = 1) +
  geom_hline(yintercept = 80, lty = 'dashed', color = 'red', size = 0.5) +
  geom_point(shape = 21, size = 3, color = '#56B4E9', fill = 'white') +
  ylim(0, 100) +
  ylab('Power') +
  xlab('Number of Subjects') 


```
### Plot power curve relY:relX:CondComp
``` {r Plot3_2}
library(ggplot2)

power_curve <- ggplot(power_all_df_2, aes(x=N_subj, y=Power_relYrelXcondcomp*100)) 

power_curve + 
  geom_errorbar(aes(ymin=power_all_df_2$Lower_relYrelXcondcomp * 100, ymax=power_all_df_2$Upper_relYrelXcondcomp * 100),  color = '#56B4E9') +
  geom_line(size = 1) +
  geom_hline(yintercept = 80, lty = 'dashed', color = 'red', size = 0.5) +
  geom_point(shape = 21, size = 3, color = '#56B4E9', fill = 'white') +
  ylim(0, 100) +
  ylab('Power') +
  xlab('Number of Subjects') 


```

### Plot power curve relY:relX:CondColl
``` {r Plot4_2}
library(ggplot2)

power_curve <- ggplot(power_all_df_2, aes(x=N_subj, y=Power_relYrelXcondcoll*100)) 

power_curve + 
  geom_errorbar(aes(ymin=power_all_df_2$Lower_relYrelXcondcoll * 100, ymax=power_all_df_2$Upper_relYrelXcondcoll * 100),  color = '#56B4E9') +
  geom_line(size = 1) +
  geom_hline(yintercept = 80, lty = 'dashed', color = 'red', size = 0.5) +
  geom_point(shape = 21, size = 3, color = '#56B4E9', fill = 'white') +
  ylim(0, 100) +
  ylab('Power') +
  xlab('Number of Subjects') 

```